VariantSpark: Population Scale Clustering of Genotype Information

### 2015-11-27 doc/publications/journal2014/paper.tex
typos and remove a sentence

\subsection*{R Implementation}
We utilise the {\sc readGT} from the {\sc VariantAnnotation} package for reading in the VCF file and extracting the the genotype matrix.  
In the supplementary material we demonstrate that this approach is approximately one minute faster than using R's built-in {\sc read.table} function, which requires  removing the first nine columns that do not contain genotypes.

>>>>

\subsection*{R Implementation}
We utilise {\sc readGT} from the {\sc VariantAnnotation} package for reading in the VCF file and extracting the genotype matrix.  
In the supplementary material we demonstrate that this approach is approximately one minute faster than using R's built-in {\sc read.table} function.
